\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{dsfont}
\usepackage{booktabs}
\usepackage{natbib}

\title{Input-Output Space Exploration}
\author{Kennedy Putra Kusumo}
\date{January 2022}


\begin{document}
	\maketitle
	
	\section{Introduction}
	The purpose of the text is to document the investigations and findings that were found in developing an experimental design technique in a specific context that is most relevant in pharmaceutical manufacturing.
	
	The experimental design technique is a model-based one. Meaning that a mathematical model is involved during experimental design and is also the ultimate goal of running the experiments (e.g., to calibrate a model).
	
	The basic idea is that there are two competing objectives associated with two sets of parameters/variables that are of interest, the so-called input and output space. The input space is defined as a set of variables which a practitioner directly (and/or conveniently) manipulate. The output space comprise of variables which the practitioners measure and interested in, but are indirectly manipulated through the input variables. As such, we shall refer to them simply as the input and output objectives.
	
	The input objective is associated with 
	
	\section{Output Space Exploration Objective}
	We present alternative criteria for operable space maximization with design of experiments, as introduced by \citet{Chen2018}.
	
	\subsection{Criteria Which Searches Over Controls}
	The goal is to find the locations of $M$ points of inputs/controls of dimension $n_x$ $\mathbf{x} \in \mathcal{X} \subset \mathbb{R}^{M \times n_x}$ that minimize or maximize a certain metric of the associated $M$ points of the outputs of dimension $n_y$ $\mathbf{y} \in \mathcal{Y} \subset \mathbb{R}^{M \times n_y}$. We assume a model (mapping) $f:\mathcal{X} \rightarrow \mathcal{Y}$ is available. The following is a list of formulations populated.
	
	\subsubsection{Maximal Spread Design}
	Spread is defined as the minimal distance between the chosen points. A formulation is as follows:
	\begin{align}
		\max_{\mathbf{x}} \	& \eta  \\
		\text{s.t. } 		& \eta \leq \lVert \boldsymbol{y}_i - \boldsymbol{y}_j \rVert, \quad i = 1 \dots M, \ j=i+1 \\
							& \boldsymbol{y}_i = f(\boldsymbol{x}_i), \quad i = 1 \dots M
	\end{align}
	
	\subsection{Criteria Which Involves Discretization of Controls}
	We assume that a finite set of candidate points $\mathbf{p}_i\in \mathbb{R}^{n}, \ i=1 \dots N$ --- possibly rescaled in the unit hypercube $[0, 1]^n$. The goal is to select a subset of $M$ points that minimize or maximize a certain metric. The following is a list of formulations and metrics populated.
	
	\subsubsection{Maximal Orthogonality Design}
	This criterion maximizes the \emph{orthogonality} of the chosen points. It involves a
	
	\subsubsection{Maximal Covering Design}
	This criterion selects $M$ centroids among the $N$ candidates in such a way that the maximal distance between any candidate point to their closest centroid is minimized. An (pure) integer programming formulation for this criterion is the following.
	\begin{align}
		\min_{\mathbf{y}, \mathbf{z}, \eta} \ & \eta  \\
		\text{s.t. } & \eta \geq \sum_{i=1}^N z_{i,j} \lVert \mathbf{p}_i - \mathbf{p}_j \rVert, \quad j = 1 \dots N  \\
					 & 1 = \sum_{i=1}^{N} z_{i,j}, \quad j = 1\dots N  \\
					 & y_i \geq z_{i,j}, \forall i,j = 1 \dots N  \\
					 & M \geq \sum_{i=1}^{N} y_i  \\
					 & y_i, z_{i,j} \in \{0, 1\}, \quad i,j = 1 \dots N
	\end{align}
	where the selected points $\mathbf{p}_i$ are those with $y_i = 1$. $z_{i,j} = 1$ indicates the closest centroid $\mathbf{p}_i$ to point $\mathbf{p}_j$. This problem is also known as the uncapacitated vertex k-center problem \citep{Cornejo2020Solving}, for which heuristics algorithms exist that could be used to warm-start the MIP solution.
	\subsubsection{Maximal Spread Design}
	Spread is defined as the minimal distance between the chosen points. $M$ points amongst the $N$ candidates are chosen to maximize spread. A pure integer programming formulation is:
	\begin{align}
		\max_{\mathbf{y}, \eta} & \eta  \\
		\text{s.t. } 			& \eta \leq \lVert \mathbf{p}_i - \mathbf{p}_j \rVert + (1 - y_i) D + (1 - y_j) D, \quad i,j = 1 \dots N  \\
								& M \geq \sum_{i=1}^N y_i  \\
								& y_i \in \{0, 1\}, \quad i = 1 \dots N
	\end{align}
	where the selected points $p_i$ are those with $y_i = 1$. The scalar $D$ is chosen and should be no smaller than the \emph{diameter} of the set of candidates points. A recommended value is $D= \max_{i,j} \lVert \mathbf{p}_i - \mathbf{p}_j \rVert$.
	
	\section{Numerical Statistics of Different Alternatives}
	\begin{table}[]
		\centering
		\begin{tabular}{lrrr}
			\toprule
			Solver & Grid Size & \# of Trials & Computational Time (s) \\
			\midrule
			\multicolumn{4}{c}{Maximal Covering (MIP)}  \\
			CPLEX                       & 25    & 3         & 0.78      \\
			CPLEX                       & 36    & 3         & 1.35      \\
			CPLEX                       & 49    & 3         & 2.73      \\
			CPLEX                       & 64    & 3         & 5.11      \\
			CPLEX                       & 81    & 3         & 8.73      \\
			CPLEX                       & 100   & 3         & 17.12     \\
			CPLEX                       & 121   & 3         & 27.43     \\
			CPLEX                       & 441   & 3         &     \\
			
			GUROBI                      & 25    & 3         &       \\
			GUROBI                      & 36    & 3         &       \\
			GUROBI                      & 49    & 3         &       \\
			GUROBI                      & 64    & 3         &       \\
			GUROBI                      & 81    & 3         &       \\
			GUROBI                      & 100   & 3         &       \\
			GUROBI                      & 121   & 3         &      \\
			GUROBI                      & 441   & 3         &     \\
			
			\multicolumn{4}{c}{Maximal Spread (MIP)}  \\
			CPLEX                       & 25    & 3         & 0.59      \\
			CPLEX                       & 36    & 3         & 0.91      \\
			CPLEX                       & 49    & 3         & 1.72      \\
			CPLEX                       & 64    & 3         & 3.12      \\
			CPLEX                       & 81    & 3         & 4.89      \\
			CPLEX                       & 100   & 3         & 7.44      \\
			CPLEX                       & 121   & 3         & 11.23     \\
			CPLEX                       & 441   & 3         & 277.75    \\
			
			GUROBI                      & 25    & 3         & 0.45      \\
			GUROBI                      & 36    & 3         & 0.94      \\
			GUROBI                      & 49    & 3         & 1.86      \\
			GUROBI                      & 64    & 3         & 3.16      \\
			GUROBI                      & 81    & 3         & 5.05      \\
			GUROBI                      & 100   & 3         & 7.85      \\
			GUROBI                      & 121   & 3         & 13.47     \\
			GUROBI                      & 441   & 3         & 359.30    \\
			
			Orthogonality               &  \\
			Convex Hull Volume          &  \\
			Ellipsoid Approximation     &  \\
			\bottomrule
		\end{tabular}
		\caption{Caption}
		\label{tab:my_label}
	\end{table}
	\bibliographystyle{plainnat}
	\bibliography{report}	
\end{document}
